Scientific Reasoning with LLMs

### 2024-11-11 docs/paper/main.tex
docs: add prompts of benchmarking experiments

\section{Experiments}
\subsection{Zero-shot and Few-shot Benchmarking}
We start by zero-shot benchmarking existing multimodal models in three simple prompt settings, partly repeating with the official evaluation suite:
\begin{enumerate}
	\item \textbf{question - choices - hint - image - task}, with the following prompt:

	\item \textbf{question - choices - hint - image - task + lecture}, with the following prompt:

	\item \textbf{question - choices - hint - image - task + lecture + solution}, with the following prompt:

\end{enumerate}

>>>>

\section{Experiments}
\subsection{Zero-shot and Few-shot Benchmarking}
We start by zero-shot benchmarking existing multimodal models in three simple prompt settings, partly repeating with the official evaluation suite:
\begin{enumerate}
	\item \textbf{question - choices - hint - image - task}, with the following prompt:
	\texttt{f'Question: {question}\n Task: {task}\n Choices: {choices}\n Hint: {hint}'}
	\item \textbf{question - choices - hint - image - task + lecture}, with the following prompt:
	\texttt{f'Question: {question}\n Task: {task}\n Choices: {choices}\n Hint: {hint}\n Lecture: {lecture}'}
	\item \textbf{question - choices - hint - image - task + lecture + solution}, with the following prompt:
	\texttt{f'Question: {question}\n Task: {task}\n Choices: {choices}\n Hint: {hint}\n Lecture: {lecture}\n Solution: {solution}'}	
\end{enumerate}
